---
title: "Geospatial Mapping of Urban Informality in Mozambique"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geospatial Mapping of Urban Informality in Mozambique}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(SAEMaputoInformality)
```

## Paper Outline
- Introduction 
- Data and methodology 
  a. Description of census data on informality 
  b.	Predicting the informality status of wage workers 
  c.	Description of census data on cell phone ownership, internet usage, and mobile money  
  d.	Description of geospatial data on cell phone coverage  
- Where in urban areas are there high shares of informal sector workers? 
- How concentrated are informal workers in particular pockets of informality? 
- To what extent do informal sector workers benefit from internet use, cell phone ownership, bank accounts, and mobile money? 
- How is informality associated with lack of cell phone coverage? 
- Conclusion  

## Predicting the informality status of wage workers
We use the Mozambique Household Budget Survey 2014/15 predict informality amongst wage workers. We define wage workers in the survey as informal if they are not enrolled in the national social security program. 

```{r, echo = FALSE, include = FALSE}



```

